%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadingLong}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheading}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
% Your LaTeX document preamble here


%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sean Flaherty} \\ \vspace{1pt}
    \small Phone: 617-416-0781 $|$
    \small Email: seanadamflaherty@gmail.com $|$
    \small Location: Boston, MA $|$
    \small Portfolio: [Your Portfolio Link]
    \vspace{1pt}
\end{center}


%-----------SUMMARY-----------
\section{Executive Summary}
\resumeSubHeadingListStart
\resumeSubheading
{JavaScript Tech Lead | Senior Front End Developer}{Computer Engineer}{Specializing in Enterprise Web Commerce Platform Integration}{react, gatsby, analytics, ndoe, async, vanilla}
\resumeItemListStart
\resumeItem{undefined}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

% Small Business Owner — Empire Mechanical Solutions, Inc — 2009 - 2017
\resumeSubheading
{Small Business Owner — Empire Mechanical Solutions, Inc — 2009 - 2017}
{Efficiently sourced parts, managed contracts, and fostered lasting relationships with clients, ensuring satisfaction and a high repeat business rate.}
{Successfully managed and operated a small automotive repair business while pursuing a college degree, serving a diverse client base. | Conducted automotive repairs, maintenance, and inspections, consistently delivering high-quality service. | Leveraged web and graphic design skills to create branding and marketing materials, establishing a strong brand identity.}
\resumeItemListStart
\resumeItem{Successfully managed and operated a small automotive repair business while pursuing a college degree, serving a diverse client base.}
\resumeItem{Conducted automotive repairs, maintenance, and inspections, consistently delivering high-quality service.}
\resumeItem{Leveraged web and graphic design skills to create branding and marketing materials, establishing a strong brand identity.}
\resumeItem{Efficiently sourced parts, managed contracts, and fostered lasting relationships with clients, ensuring satisfaction and a high repeat business rate.}
\resumeItemListEnd


% Senior Web Developer — Therefore Interactive — 2021 - 2023
\resumeSubheading
{Senior Web Developer — Therefore Interactive — 2021 - 2023}
{Spearheaded the transition to a decoupled architecture, connecting CMS with modern Front-End frameworks (Gatsby, React, Vue, Next) for robust, accessible web experiences.}
{Led as a JavaScript Tech Lead for full-stack web development projects, collaborating with a diverse client base, including government form microsites and financial trading platforms. | Architected modern web solutions, optimizing e-commerce systems and enhancing user experiences, using technologies like React, TypeScript, and JavaScript.}
\resumeItemListStart
\resumeItem{Led as a JavaScript Tech Lead for full-stack web development projects, collaborating with a diverse client base, including government form microsites and financial trading platforms.}
\resumeItem{Architected modern web solutions, optimizing e-commerce systems and enhancing user experiences, using technologies like React, TypeScript, and JavaScript.}
\resumeItem{Spearheaded the transition to a decoupled architecture, connecting CMS with modern Front-End frameworks (Gatsby, React, Vue, Next) for robust, accessible web experiences.}
\resumeItemListEnd


% Intermediate Web Developer — OPIN Digital — 2019 - 2021
\resumeSubheading
{Intermediate Web Developer — OPIN Digital — 2019 - 2021}
{Applied advanced techniques to optimize and integrate distributed e-commerce systems, leveraging content management systems, async API calls, and custom modules.}
{Specialized as a JavaScript expert and tech lead, providing company-wide JS training and advocating a component-based design approach. | Achieved the highest billing developer for two years, serving 30-50+ clients annually.}
\resumeItemListStart
\resumeItem{Specialized as a JavaScript expert and tech lead, providing company-wide JS training and advocating a component-based design approach.}
\resumeItem{Achieved the highest billing developer for two years, serving 30-50+ clients annually.}
\resumeItem{Applied advanced techniques to optimize and integrate distributed e-commerce systems, leveraging content management systems, async API calls, and custom modules.}
\resumeItemListEnd


% Junior Software Engineer — Black Duck Software — 2015-2016
\resumeSubheading
{Junior Software Engineer — Black Duck Software — 2015-2016}
{Identified and resolved runtime issues, implementing efficient solutions.}
{Upgraded Java Spring Framework to Java 8, enhancing web application performance.}
\resumeItemListStart
\resumeItem{Upgraded Java Spring Framework to Java 8, enhancing web application performance.}
\resumeItem{Identified and resolved runtime issues, implementing efficient solutions.}
\resumeItemListEnd


% Jr Electromechanical Engineer — Rypos — 2014-2015
\resumeSubheading
{Jr Electromechanical Engineer — Rypos — 2014-2015}
{Contributed to the design and testing of the next-generation model, including optical isolation control circuits.}
{Collaborated on integrating electromechanical components in distributed systems.}
\resumeItemListStart
\resumeItem{Collaborated on integrating electromechanical components in distributed systems.}
\resumeItem{Contributed to the design and testing of the next-generation model, including optical isolation control circuits.}
\resumeItemListEnd


% ASE Certified Dealership Technician — Herb Chambers Honda Infiniti — 2007 - 2010
\resumeSubheading
{ASE Certified Dealership Technician — Herb Chambers Honda Infiniti — 2007 - 2010}
{Held a licensed State (MA) Vehicle Safety and Emissions Inspector certification.}
{Performed vehicle maintenance and repair, specializing in electronic and engine performance.}
\resumeItemListStart
\resumeItem{Performed vehicle maintenance and repair, specializing in electronic and engine performance.}
\resumeItem{Held a licensed State (MA) Vehicle Safety and Emissions Inspector certification.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]

    \small{\item{
    \textbf{General}{Enterprise Systems Architecture, Dev Ops, Full Stack Web Development, Accessible Design, Test Driven Development, Troubleshooting, Problem Solving, Teaching, Mentoring, Technical Writing} \
    }}

    \small{\item{
    \textbf{Web Application Development}{JavaScript Technical Lead, E-Commerce Integration, Clean, Readable Code} \
    }}

    \small{\item{
    \textbf{Languages}{JavaScript, TypeScript, React, Python, EScript, Node.Js, Java, Verilog, PHP, HTML, CSS, SCSS, Ruby, C, C++, Python} \
    }}

    \small{\item{
    \textbf{Technologies}{React 18, Gatsby, Redux, Gitlab, Vue.Js, Express, Apollo, Django, Next, GraphQL, Spring, Webpack, Angular, Electron, Linux, Debian, Ruby On Rails, BASH, Shell Scripting, Docker, Jira, Google Analytics, Solr, Continuous Integration, Continuous Deployment Pipelines} \
    }}
\end{itemize}


% Your LaTeX document closing here

% Your LaTeX document closing here
\end{document}
